High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-04 paper/main.tex
updated cartoon brains figure

@@

\begin{figure}[hp]
  \centering
  \includegraphics[width=\textwidth]{figs/decode_level}
  \caption{\textbf{Across-participant decoding accuracy varies with
      correlation order and cognitive engagement.}
    \textbf{a. Decoding accuracy as a function of order: PCA.}
    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies are averaged over all
    kernel shapes and widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error bars
    denote 95\% confidence intervals across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upwards
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed test, thresholded at
    $p < 0.05$).  The circled values represent the maximum decoding
    accuracy within each experimental condition.
    \textbf{b. Normalized decoding accuracy as a function of order:
      PCA.}  This panel displays the same results as Panel a, but here
    each curve has been normalized to have a maximum value of 1 and
    and a minimum value of 0 (including the upper and lower bounds of
    the respective 95\% confidence intervals).  Panels a and b used
    PCA to project each high-dimensional pattern of dynamic
    correlations onto a lower-dimensional space.  \textbf{c.  Decoding
      accuracy as a function of order: eigenvector centrality.} This
    panel is in the same format as Panel a, but here eigenvector
    centrality has been used to project the high-dimensional patterns
    of dynamic correlations onto a lower-dimensional space.
    \textbf{d. Noramlized decoding accuracy as a function of order:
      eigenvector centrality.} This panel is in the same format as
    Panel b, but here eigenvector centrality has been used to project
    the high-dimensional patterns of dynamic correlations onto a
    lower-dimensional space.}
  \label{fig:decoding}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figs/most_abs}
  \caption{\textbf{Top terms associated with the endpoints of the
      strongest correlations.}  Each color corresponds to one order of
    correlations, averaged across participants and time. The inflated
    brain plots display the locations of the endpoints of the 10
    strongest (absolute value) correlations at each order, projected
    onto the cortical surface~\citep{CombEtal19}.  The lists of terms
    on the right display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
    for each order.  Each row displays data from a different
    experimental condition.  Additional maps and their corresponding
    Neurosynth terms may be found in the \textit{Supplementary
      materials} (intact: Figure S1; paragraph: Figure S2; word:
    Figure S3; rest: Figure S4).}
  \label{fig:neurosynth}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/direction_of_field}
  \caption{\textbf{Direction of the field (adapted from~\citep{Turk13}).} The evolution of fMRI analyses started with
    univariate activation, which refers to
    the average amplitude of BOLD activity evoked by events of an
    experimental condition. Next, multivariate classifiers are trained
    on patterns of activation across voxels to decode distributed
    representations for specific events. The next, resting
    connectivity, is the temporal correlation of one or more seed
    regions with the remainder of the brain during rest. Additionally,
    task-based connectivity examines how these correlations differ by
    cognitive state. Following this increasing trajectory of
    increasing complexity, full connectivity considers all pairwise
    correlations in the brain, most commonly at rest.  Next, dynamic
    full connectivity considers how full connectivity changes over
    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
  \label{fig:direction_of_field}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.65\textwidth]{figs/direction_of_field}
  \caption{\textbf{Neural patterns.} The evolution of fMRI analyses started with
    univariate activation, which refers to
    the average amplitude of BOLD activity evoked by events of an
    experimental condition. Next, multivariate classifiers are trained
    on patterns of activation across voxels to decode distributed
    representations for specific events. The next, resting
    connectivity, is the temporal correlation of one or more seed
    regions with the remainder of the brain during rest. Additionally,
    task-based connectivity examines how these correlations differ by
    cognitive state. Following this increasing trajectory of
    increasing complexity, full connectivity considers all pairwise
    correlations in the brain, most commonly at rest.  Next, dynamic
    full connectivity considers how full connectivity changes over
    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
  \label{fig:direction_of_field}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/decode_level}
  \caption{\textbf{Across-participant decoding accuracy varies with
      correlation order and cognitive engagement.}
    \textbf{a. Decoding accuracy as a function of order: PCA.}
    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies are averaged over all
    kernel shapes and widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error bars
    denote 95\% confidence intervals across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upwards
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed test, thresholded at
    $p < 0.05$).  The circled values represent the maximum decoding
    accuracy within each experimental condition.
    \textbf{b. Normalized decoding accuracy as a function of order:
      PCA.}  This panel displays the same results as Panel a, but here
    each curve has been normalized to have a maximum value of 1 and
    and a minimum value of 0 (including the upper and lower bounds of
    the respective 95\% confidence intervals).  Panels a and b used
    PCA to project each high-dimensional pattern of dynamic
    correlations onto a lower-dimensional space.  \textbf{c.  Decoding
      accuracy as a function of order: eigenvector centrality.} This
    panel is in the same format as Panel a, but here eigenvector
    centrality has been used to project the high-dimensional patterns
    of dynamic correlations onto a lower-dimensional space.
    \textbf{d. Noramlized decoding accuracy as a function of order:
      eigenvector centrality.} This panel is in the same format as
    Panel b, but here eigenvector centrality has been used to project
    the high-dimensional patterns of dynamic correlations onto a
    lower-dimensional space.}
  \label{fig:decoding}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/most_abs}
  \caption{\textbf{Top terms associated with the endpoints of the
      strongest correlations.}  Each color corresponds to one order of
    correlations, averaged across participants and time. The inflated
    brain plots display the locations of the endpoints of the 10
    strongest (absolute value) correlations at each order, projected
    onto the cortical surface~\citep{CombEtal19}.  The lists of terms
    on the right display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
    for each order.  Each row displays data from a different
    experimental condition.  Additional maps and their corresponding
    Neurosynth terms may be found in the \textit{Supplementary
      materials} (intact: Figure S1; paragraph: Figure S2; word:
    Figure S3; rest: Figure S4).}
  \label{fig:neurosynth}
\end{figure}

@@
